Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-17 unusedFigsTables.tex
Cleaning up some figures and fixing gitignore

 \begin{figure}
   \centering
     \includegraphics[width=0.5\textwidth]{unused-figs/3dcolcache}
     \caption{A 3D projection of a delay-coordinate embedding of the trace
 from Figure~\ref{fig:cache} with a delay ($\tau$) of 100,000 instructions.
 }
 \label{fig:embedding}
 \end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdipcfull}
                \caption{SVD IPC without coloring}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdipcregimescolored}
                \caption{SVD IPC with coloring}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD Full Time Series }\label{fig:svdFull}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdregime2prediction}
                \caption{SVD Regime 2 LMA Prediction}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdregime2predictionFULL}
                \caption{SVD Regime 2 LMA Prediction with Full Time Series}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD Regime 2 LMA Prediction Figures }\label{fig:svdregime2prediciton}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdPrediction}
                \caption{SVD Regime 5 LMA Prediction}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/svdPredictionFull}
                \caption{SVD Regime 5 LMA Prediction with Full Time Series}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD Regime 5 LMA Prediction Figures }\label{fig:svdregime5prediciton}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/colfullts}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/colshortts}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}

@@

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{figs/colPredShortTS}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{figs/colPredfullTS}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/gccfullts}\caption{403.gcc full time series}
\label{default}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/regime1}\caption{SVD IPC Regime 1 Time Series}
\label{default}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/regime2}\caption{SVD IPC Regime 2 Time Series}
\label{default}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/regime5}\caption{SVD IPC Regime 5 Time Series}
\label{default}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{figs/regime6}\caption{SVD IPC Regime 6 Time Series}
\label{default}
\end{center}
\end{figure}

>>>>

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/svdipcfull}
                \caption{SVD IPC without coloring}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/svdipcregimescolored}
                \caption{SVD IPC with coloring}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD Full Time Series }\label{fig:svdFull}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/svdregime2prediction}
                \caption{SVD Regime 2 LMA Prediction}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/svdregime2predictionFULL}
                \caption{SVD Regime 2 LMA Prediction with Full Time Series}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD Regime 2 LMA Prediction Figures }\label{fig:svdregime2prediciton}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/svdPrediction}
                \caption{SVD Regime 5 LMA Prediction}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/svdPredictionFull}
                \caption{SVD Regime 5 LMA Prediction with Full Time Series}
                \label{fig:svdFullColored}
        \end{subfigure}
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
         \caption{SVD Regime 5 LMA Prediction Figures }\label{fig:svdregime5prediciton}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/colfullts}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/colshortts}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}

@@

\begin{figure}
        \centering
        \begin{subfigure}{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/colPredShortTS}
                \caption{col IPC  Full Time Series}
                \label{fig:gull}
        \end{subfigure}%
        \newline
        ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
          %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{\textwidth}
                \includegraphics[width=\textwidth]{unused-figs/colPredfullTS}
                \caption{col IPC  Short Time Series for structure illustration}
                \label{fig:svdFullColored}
        \end{subfigure}

@@

%\begin{figure}[htbp]
%\begin{center}
%\includegraphics[width=\textwidth]{unused-figs/%colPredictionVariation.pdf}
%\end{center}
%\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{unused-figs/gccfullts}\caption{403.gcc full time series}
\label{default}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{unused-figs/regime1}\caption{SVD IPC Regime 1 Time Series}
\label{default}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{unused-figs/regime2}\caption{SVD IPC Regime 2 Time Series}
\label{default}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{unused-figs/regime5}\caption{SVD IPC Regime 5 Time Series}
\label{default}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\textwidth]{unused-figs/regime6}\caption{SVD IPC Regime 6 Time Series}
\label{default}
\end{center}
\end{figure}
